biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-10-02 paper/PaperTRA/PaperTRA.Rmd
deflation rate

```{r summaryall, message=FALSE, warning=FALSE}
summaryall = summary1 |> left_join(summary22) |> 
  select(c(1, 2, 6, 7, 8, 13)) |> 
  mutate(CO2eq = co2 + CO2eq,
         value1 = monet/10 + Value, # this is NOT CORRECT, need to inflate - see original table
         value10 = monet + Value*10) |> # this is NOT CORRECT, need to deflate
  select(Estrategia, LTS, CO2eq, value1, value10)

@@

<!-- correct the € numbers after inflation -->
Shifting from car to cycling + PT can reduce annual CO~2~eq emissions by 14,000 to 36,000 tons per year, 
and the 10-year socio-environmental benefits account for €238 to €626 million, depending on the cycling targets.

>>>>

```{r summaryall, message=FALSE, warning=FALSE}
summary0 = readRDS("load/HEAT_aml_results.Rds") |> slice_tail(n = 4)
rate = ((1+0.03)^10)/((1+0.05)^10) # inflation rate 3% discount rate 5%

summaryall = summary1 |> left_join(summary22) |> 
  mutate(Code = c(3304, 3404, 3310, 3410)) |> 
  left_join(summary0 |> select(Code, Economic), by = "Code") |> 
  select(c(1, 2, 6, 7, 8, 13, 15)) |> 
  mutate(CO2eq = co2 + CO2eq,
         value1 = Economic/1000 + Value, # this is CORRECT
         value10 = monet + Value*10*rate) |> # this is CORRECT
  select(Estrategia, LTS, CO2eq, value1, value10)

@@

<!-- separate the Socio impacts from the Environemtal ones? It shouldn't be ok to sum them -->
Shifting from car to cycling + PT can reduce annual CO~2~eq emissions by 14,000 to 36,000 tons per year, 
and the 10-year socio-environmental benefits account for €235 million to €620 million, depending on the cycling targets.

### 2023-10-02 paper/PaperTRA/PaperTRA.tex
update 1yr SE
deflation rate

\caption{\label{tab:summaryall}\label{summaryall}Summary of the avoided CO2eq emmissions (ton/year) and the estimated social and environmental benefits (monetized in thousand €) by replacing car trips with cycling in combination with PT.}
\centering
\begin{tabular}[t]{ll>{\raggedleft\arraybackslash}p{8em}>{\raggedleft\arraybackslash}p{8em}>{\raggedleft\arraybackslash}p{8em}}
\toprule
Target & Routing & Avoided CO2eq (tons) & SE Benefits 1yr (k€) & SE Benefits 10yrs (k€)\\
\midrule
4\% & safe & 14 513 & 1 655 & 244 516\\
4\% & direct & 14 713 & 1 677 & 238 248\\
10\% & safe & 35 819 & 4 022 & 626 096\\
10\% & direct & 36 207 & 4 061 & 609 073\\
\bottomrule
\end{tabular}
\end{table}

Shifting from car to cycling + PT can reduce annual
CO\textsubscript{2}eq emissions by 14,000 to 36,000 tons per year, and
the 10-year socio-environmental benefits account for €238 to €626
million, depending on the cycling targets.

>>>>

\caption{\label{tab:summaryall}\label{summaryall}Summary of the avoided CO2eq emmissions (ton/year) and the estimated social and environmental benefits (monetized in thousand €) by replacing car trips with cycling in combination with PT.}
\centering
\begin{tabular}[t]{ll>{\raggedleft\arraybackslash}p{8em}>{\raggedleft\arraybackslash}p{8em}>{\raggedleft\arraybackslash}p{8em}}
\toprule
Target & Routing & Avoided CO2eq (tons) & SE Benefits 1yr (k€) & SE Benefits 10yrs (k€)\\
\midrule
4\% & safe & 14 513 & 27 299 & 242 024\\
4\% & direct & 14 713 & 26 572 & 235 706\\
10\% & safe & 35 819 & 69 938 & 620 094\\
10\% & direct & 36 207 & 67 956 & 602 972\\
\bottomrule
\end{tabular}
\end{table}

Shifting from car to cycling + PT can reduce annual
CO\textsubscript{2}eq emissions by 14,000 to 36,000 tons per year, and
the 10-year socio-environmental benefits account for €235 million to
€620 million, depending on the cycling targets.
